Dependent Object Types

### 2012-08-30 doc/candidacy/report.tex
ex

First, we show how to encode monomorphic functions into the
calculus. The paper goes further and generalizes the encoding to
system $F_{<:}$

>>>>

First, we show how to encode monomorphic functions into the
calculus. The paper goes further and generalizes the encoding to
system $F_{<:}$. A $\lambda$-abstraction $\lambda ( x : T )\; t$ is
represented as a class with an abstract member \code!arg! for the
function argument:
\begin{lstlisting}
[x: {arg: T}| fun = [res = $t'$]]
\end{lstlisting}
$t'$ corresponds to term $t$ in which all occurrences of $x$ are
replaced by \code!$x$.arg!. We cannot directly access \code!arg! on
the right-hand side of \code!fun!: this wouldn't be ``contractive'',
because \code!arg! might not be initialised before \code!fun!. Hence,
we pack $t'$ in another class to ensure contractiveness. Now, an
application $g(e)$ gets decomposed into three subsequent steps:
\begin{lstlisting}
$\nu\,$g$_{app}$  <- g & [arg = e];
$\nu\,$g$_{eval}$ <- g$_{app}$.fun;
g$_{eval}$.res
\end{lstlisting}
First we instantiate function \code!g! with a concrete argument
yielding a thunk \code!g$_{app}$!. Then we evaluate this thunk by
creating an instance \code!g$_{eval}$! of it. Finally we extract the
result by querying field \code!res! of \code!g$_{eval}$!.
